Automatic Metadata Generation for Fish Specimen Image Collections {\footnotesize \thanks{Research supported by NSF OAC \#1940233 and \#1940322.} }

### 2022-09-15 legacy_code/paper/jcdl.tex
Create legacy-code folder with initial code

%abstract can be shortened a good bit.
%can offer an alternative manana..
\begin{abstract}
Metadata is a key data source, particularly for researchers seeking to apply machine learning (ML) to the vast collections of digitized specimens. Unfortunately, the available metadata is often sparse and, at times, erroneous. Additionally, it is prohibitively expensive to address these limitations through traditional, manual means.
This paper reports on research that applies machine-driven approaches to
analyzing digitized fish images and extracting various important
features from them. The digitized fish specimens are being analyzed as part of the Biology Guided Neural Networks (BGNN) initiative, which is developing a novel class of artificial neural networks using phylogenies and anatomy ontologies. Automatically generated metadata is crucial for identifying
the high-quality images needed for the neural network's predictive analytics.
%predictive analytics?
Methods that  combine ML and image informatics techniques allow us to rapidly enrich the existing metadata associated with the
7,244 images from the Illinois Natural History Survey (INHS) used in our
study. The sample
images also have 22 manually generated metadata properties, which
can be used for comparison.  Results show we can accurately generate many key metadata properties relevant to the
BGNN project such as: fish quantity and orientation,  image scaling based on
ruler identification and measurement, and general image quality metrics
(e.g.\ brightness and contrast). Results also show we can also accurately generate bounding boxes and segmentation masks for fish, which are needed for subsequent machine learning analysis.
%to confirm list of six properties.
%x, y, z = any other key results. jg will add from results section, unless someone else does first. 
The automatic process out-performs humans in terms of time and labor cost,
as well as accuracy, and provides a novel solution for leveraging digitized
specimens in ML. This research demonstrates the ability of computational
methods to enhance the digital library services associated with
the tens of thousands of digitized specimens stored in open-access
repositories world-wide.
%world wide [*across the globe] or we may not even need this part as open access is global access

% OLD text - Over the last several decades advances in computing, imaging, and cyberinfrastructure have had a major impact on scientific research and discovery. One area of considerable activity is the digitization of the biological specimens that have been acquired worldwide by museums and other research institutions, undertakings that have produced large image collections.The metadata that is vital for subsequent ML, analysis and scientific discovery based on these specimen image repositories is often unavailable, sparse or incorrect. As a step towards improving metadata in specimen research image collections, our team is developing methods for automatically analyzing fish images to extract a variety of important features. These fish specimens are being studied for a larger project entitled Biology Guided Neural Networks (BGNN), which is developing a novel class of artificial neural networks that can exploit the machine readable and predictive knowledge about biology that is available in specimen images, phylogenies and anatomy ontologies. Using a combination of ML and image informatics tools and techniques, we can accurately determine metadata such as fish quantity and location within images, fish orientation and other quantitative fish features, image scaling based on ruler identification and measurement, and general image quality metrics for a substantial number of the images being used in the BGNN project.Our goal is to develop image metadata generation methods that both support the research underway within the BGNN project, and provide a framework for future technology developments that can be deployed by repository curators to improve and bolster the metadata they provide with their specimen images. A longer term goal is to extend the image analysis methods for computing quantitative features in support of specific biological investigations.
\end{abstract}

@@

\section{Introduction}
% Moving teaser since this template doesn't actually ask for one
Over the last several decades advances in computing, imaging, and cyberinfrastructure have supported the growth of digital natural history collections, many of which contain specimen images~\cite{beaman2012mass}. Additionally, initiatives, such as the National Science Foundation’s Advancing Digitization of Biodiversity Collections (ADBC) program,
% (which ran for nearly a decade),
have supported the digitization and curation of tens of thousands of biological specimens~\cite{page2015digitization}. These digitized specimens are generally accessible through global, open-access repositories that support digital library services, such as browsing, search and retrieval, and preservation. The digitized renderings of these rich collections permit researchers, educators, students, and the general public to examine biological specimens
on a previously unattainable scale. Moreover, the digitized instantiations present a pathway for applying ML and making new scientific discoveries.

Unfortunately, potential scientific advances are hindered by image quality
problems and the lack of accurate and pertinent metadata
associated with the image collections.
Poor quality images (e.g.\ low contrast, inadequate lighting,
out-of-focus or cluttered visual arrangements) provide inadequate input
for automated
image analysis and ML algorithms and lead to inferior
computational results.
In order to perform quantitative morphometric analysis of the specimens,
the physical scale of the images (\(\frac{\mathrm{pixels}}{\mathrm{cm}}\)) is needed; thus
requiring the ability to identify and measure rulers in the images.
Many specimen collections do include Darwin Core metadata~\cite{biodiv_info_standards}, detailing
specimen taxon, geographic location, and several other descriptive aspects.
Additionally, some digitization efforts record technical metadata, detailing imaging specifications. While these types of metadata are helpful for a
human examining several images at a time, they are insufficient for researchers seeking to apply computational methods %ML? or okay here
to examine thousands of images
to determine if, for example, a specific fish grows to different lengths
in different habitats, or the temporal evolution of an anatomical feature,
e.g.~the size of a dorsal fin.
\begin{figure}[t]
  \centering
  % \includegraphics[width=.31\linewidth]{images/INHS_FISH_100314}
  % \hspace{1mm}
  \includegraphics[width=.95\linewidth]{images/INHS_FISH_100682}
  % \hspace{1mm}
  % \includegraphics[width=.31\linewidth]{images/INHS_FISH_100020}
  \caption{An image from the Illinois Natural History Survey (INHS) collection.}
  \label{fig:INHS_examples}
\end{figure}

Since digital collections may each contain tens of thousands of images, manually producing image-related metadata for each digitized specimen is both labor- and time-intensive and prohibitively expensive. Methods for automatically computing metadata are therefore needed to fully exploit biological image repositories for scientific discovery.
%we are both extracting and calculating. Just to double check then, our definition/understanding of computing here includes both of these, or should we focus on extraction, with the idea that calculating is the extra novel thing added, the application of math-the groovy stuff you guys added.  
As a step towards improving metadata in research specimen image collections, members of Drexel University's Metadata Research Center are developing methods to automatically analyze fish images and
extract a set of data features that provide important metadata about the
digitized specimens.
The research is being conducted as part of the Biology Guided Neural Networks (BGNN) project, which is developing a novel class of artificial neural networks that exploit machine readable and predictive knowledge associated with specimen images, phylogenies and anatomy ontologies.
Using a combination of ML and image informatics 
techniques,
%tools and [okay to just say image informatics techniques instead of "image informatics tools and techniques" - thinking techniques implies tools.]
we can accurately determine general image quality and metadata, such as fish quantity and location within images, fish orientation, and
image scaling based on ruler identification and measurement. Image scaling
allows us to compute quantitative features about the fish specimens, such
as their length and area.  In order to test and validate our methods, they
have been  applied to a set of \(7,244\)
images drawn from the Illinois Natural History Survey (INHS) Collection~\cite{INHS}.
Figure \ref{fig:INHS_examples} presents a typical image used in our
study.
%Dave/Joel, the section above, from "we can accurately ..." to the figures" to me is more results. I guess it's okay to give this in introduction. Just wanted to raise this point. I sometimes give a paraphrase too, but just good to see if it is a little too much or okay with you both. I think it's okay as I re-read it, but good to have someone check.
The following section of the paper provides contextual background for this work, followed by the research goals and objectives, and a review of our research methods. Next, the results, along with discussion, are presented. The conclusion highlights key findings and identifies next steps.

\section{Related Work}
\subsection{Metadata for Natural History Image Collection}
%question/comment - we need to keep in mind we are deal with digitized specimens, not simply digital, in other words, the artifacts themselves are digital version of physical, not like an x-ray, where the image is digital from the start.  
A number of different metadata standards have been applied to support the description and access of digitized scientific images. The Darwin Core (DwC)~\cite{biodiv_info_standards}, developed specifically to describe biological diversity data, is one of the most popular standards for such efforts. It is an extension of the Dublin Core's DCMI Metadata Terms~\cite{dc_terms}.
The Audubon Core~\cite{audub_core}, which supports the discoverability, dissemination, and use of data related to biological organisms (including 3--D digitized specimens), is a DwC extension that has become more popular. All of these descriptive standards and extensions include metadata properties for taxon, geographic location, and other important specimen content, and have been developed primarily from the perspective of a human curator. In other words, their application anticipates that a curator or data entry staff will manually generate metadata, drawn from acquisition logs or original specimen labels. This task is labor intensive, and the metadata associated with each digital rendering is generally sparse and more prone to human error, placing limitations on a researcher seeking to apply ML to the image and the metadata for scientific research.

This limitation is magnified when trying to assess the actual quality of the digitized specimen. Descriptive-oriented standards support search and retrieval, and the biodiversity community has advocated for data fitness standards \cite{chapman2020developing}. This point is also emphasized by
Wieczorek et al.~\cite{wieczorek2012darwin} in their report on the variety of DwC metadata extensions needed to meet growing community concerns and
requirements, including data quality and fitness. Even so, metadata describing image quality is severely limited and generally missing. This point is addressed in detail by Leipzig et al.~\cite{leipzig2021biodiversity} and serves as the rationale for Tulane University's effort to manually capture
content for 22 metadata properties that characterize digitized specimen image quality. Their work is being conducted in connection with the larger BGNN initiative, and the current process is costly in terms of labor and time, prone to human error and inconsistencies, and underscores the need to
explore automatic metadata generation methods.
%Fish species dataset in Pakistan Shah 2019 \cite{Shah2019FishPakFS}
\subsection{Automatic Metadata Generation}
Automatic metadata generation advances covering both descriptive and technical metadata are relevant to the research presented in this paper. Automatic metadata generation of descriptive bibliographic data has been a research focus for close to 20 years \cite{liddy2002automatic,greenberg2004metadata,cardinaels2005automating,paynter2005developing}. Researchers have applied support vector machine (SVM) approaches~\cite{han2003automatic}, and associated networks to address sparse and incomplete metadata~\cite{rodriguez2009automatic}, and various successes are integrated into day-to-day workflows. Heidorn, et al.~\cite{heidorn2008automatic} demonstrated the use of optical character recognition (OCR) to extract specimen information from the original typed and often hand-annotated labels that are digitized along with herbarium collection holdings. The extracted information was encoded in the DwC metadata associated with the specimen's digitized rendering. There has also been some success with extracting descriptive cartographic information from maps~\cite{manso2004automatic}. While descriptive metadata covers taxon, geographic location, and other important aspects, and may even record the image format; extensive use of automatic processes are still limited. More significantly, descriptive metadata does not sufficiently addressed data quality.

@@

application of technology both for marine science, in the study of aquatic

@@

combinations of features extraction, input classifiers and clustering

@@

types of fish with a 92\% accuracy.

@@

accuracy when identifying 15 different fish in challenging underwater

@@

@@

The research reviewed above involves image features extraction and
artificial intelligence; although the researchers have not applied these
approaches to the burgeoning collections of digitized specimens
accessible in open repositories. Our research addresses this need by
applying ML and image informatics techniques to extract key
metadata properties from fish specimen images and computing
higher-level metadata based on these initial results.
Our goals and objectives our presented below.

\begin{comment}
Our work stands apart from previous work in that we are
addressing a different need: lack of metadata is impeding scientific studies.
Our focus and motivation are different.
Effectively doing the computational pre-processing
that will enable further downstream analyses.

@@

Digitized specimens accessible in open-access repositories provide a rich,
extensive data source for ML and scientific discovery.
These resources, however, remain largely untapped due to image quality
issues and metadata limitations.
The overall goal of our work addresses this need by
% combining ML and image informatics techniques to produce
developing a computational
% . The overall goal of our research is to offer a machine-driven [*novel/innovative?? blah...]
alternative to the current manual metadata generation process, one that is
prohibitively costly in both terms of labor and time. Additionally, our
methods collectively provide a novel and general approach to computing
higher-level metadata that will support scientific inquiry based
on the analysis of specimen image collections.

@@

\item Investigate image processing at the pixel level.
Pilot testing found that \verb|detectron| under-segmented the detected objects
with tightly enclosing bounding boxes. We will determine if
pixel analysis methods commonly found in image informatics may produce
more accurate bounding boxes and object masks.
% background as part of the fish, or the
% bounding box may clip away part(s) of the fish with
The specific aims of this objective are to:
%not sure we have to list all the details, but something like the below, with the 4 aspects of pixel analysis we tested/investigate/experimented with

@@

\item
Automatically determine when modified methods fail and detectron values
should be used as is.
% Developing a fallback approach for when flood fill operations behave unexpectedly the image is too washed out.
\end{enumerate}

\begin{figure}[t]
  \centering
 % \includegraphics[width=.45\linewidth]{images/teaser1_crop}
  % \hspace{5mm}
  \includegraphics[width=.95\linewidth]{images/teaser2_crop}
  \caption{Initial object detection on a specimen image using Detectron2~\cite{wu2019detectron2}.}
  \label{fig:teaser}
\end{figure}

@@

%In order to address the need for fish specimen image metadata that can support scientific investigations we have begun the deployment of both off-the-shelf and custom-written software that automatically generates a variety of metadata from a publicly-available biological image repository.  The types of metadata being produced are related to image quality, content and scale, and should provide the information necessary for advanced quantitative studies of the digitized specimens.

The automated metadata generation methods for our project were developed to work on a specific set of images, the INHS\ Fish Collection~\cite{INHS}.  Most of these images have been configured, produced and acquired with a standard procedure.  The images used for our study contain one fish placed on a bright, white background and contain an information tag and the same ruler.  See Figure \ref{fig:INHS_examples} for an example image from the collection. While training and focusing our system on images with very similar compositions and visual properties may limit its immediate applicability, our efforts demonstrate the potential that ML and image informatics techniques have for automatically generating metadata for biological specimen image collections in general.

@@

\subsection{Detectron}
A prerequisite task to performing any advanced metadata property generation
is finding the specimens (and other relevant objects) within the collection
images. Object detection has been a broadly active field of study in recent
years \cite{zou2019object}, and has resulted in a number of well-tested, purpose-built architectures. We elected to use Facebook AI Research's (FAIR)
\verb|detectron| tool \cite{wu2019detectron2}, and specifically its implementation of the Mask R-CNN architecture \cite{he2018mask}, for object detection in our project, given its many flexible and robust capabilities.
\verb|detectron| is built on \verb|pytorch|~\cite{NEURIPS2019_9015} and provides a relatively straightforward method for training on COCO~\cite{DBLP:journals/corr/LinMBHPRDZ14} format datasets. It is able to handle any number of object classes, and can classify an arbitrary number of objects within a given image. We chose \verb|detectron| for its relative ease of use compared to lower level libraries, and its implementation of powerful architectures developed by FAIR.
For our project, we use it to identify five object classes: fish, fish eyes, rulers, and the numbers 2 and 3 on rulers,
as shown in Figure \ref{fig:teaser}. Objects with a 30\% confidence score or higher are maintained for analysis.

@@

\begin{table*}[t]
    \centering
    \caption{Metadata properties (* indicates higher order derived properties)}
    \label{tab:properties}
    \begin{tabular}{cccp{0.5\linewidth}}
        \toprule
        \textbf{Property} & \textbf{Association} & \textbf{Type} & \textbf{Explanation}\\
        \midrule
        \verb|has_fish| & Overall Image & Boolean & Whether a fish was found in the image.\\
        \verb|fish_count| & Overall Image & Integer & The quantity of fish present.\\
        \verb|has_ruler| & Overall Image & Boolean & Whether a ruler was found in the image.\\
        \verb|ruler_bbox| & Overall Image & 4 Tuple & The bounding box of the ruler (if found).\\
        \verb|scale|* & Overall Image & Float & The scale of the image in \(\frac{\mathrm{pixels}}{\mathrm{cm}}\).\\
        \verb|bbox| & Per Fish & 4 Tuple & The top left and bottom right coordinates of the bounding box for a fish.\\
        \verb|background.mean| & Per Fish & Float & The mean intensity of the background within a given fish's bounding box.\\
        \verb|background.std| & Per Fish & Float & The standard deviation of the background within a given fish's bounding box.\\
        \verb|foreground.mean| & Per Fish & Float & The mean intensity of the foreground within a given fish's bounding box.\\
        \verb|foreground.std| & Per Fish & Float & The standard deviation of the foreground within a given fish's bounding box.\\
        \verb|contrast|* & Per Fish & Float & The contrast between foreground and background intensities within a given fish's bounding box.\\
        \verb|centroid| & Per Fish & 4 Tuple & The centroid of a given fish's bitmask.\\
        \verb|primary_axis|* & Per Fish & 2D Vector & The unit length primary axis (eigenvector) for the bitmask of a given fish.\\
        \verb|clock_value|* & Per Fish & Integer & Fish's primary axis converted into an integer ``clock value'' between 1 and 12.\\
        \verb|length|* & Per Fish & Float & The length of a fish in \(\frac{\mathrm{pixels}}{\mathrm{cm}}\).\\
        \verb|mask| & Per Fish & 2D Matrix & The bitmask of a fish in 0's and 1's.\\
        \verb|pixel_analysis_failed| & Per Fish & Boolean & Whether the pixel analysis process failed for a given fish. If \verb|true|, \verb|detectron|'s mask and bounding box were used for metadata generation.\\
        \verb|score| & Per Fish & Float & The percent confidence score output by \verb|detectron| for a given fish.\\
        \verb|has_eye| & Per Fish & Boolean & Whether an eye was found for a given fish.\\
        \verb|eye_center| & Per Fish & 2 Tuple & The centroid of a fish's eye.\\
        \verb|side|* & Per Fish & String & The side (i.e.\ \verb|'left'| or \verb|'right'|) of the fish that is facing the camera (dependent on finding its eye).\\
      \bottomrule
\end{tabular}
\end{table*}

@@

\subsubsection{Adjusting the Bounding Box}
With an accurate mask generated, it is then necessary to check whether the bounding box needs to be expanded or shrunk along any of its edges.
Expansion is done first, by checking whether any edge intersects with any of the foreground mask pixels. If one does, it is expanded out by 1 pixel. If any edges are expanded, the whole process of masking and expansion is repeated to account for any changes in average intensities. Once no edges contain foreground pixels, the bounding box is then shrunk.
% This process is more efficient as all that is required is to shrink
Each edge is contacted by one pixel up until it contain one or more foreground pixels. Once the shrinkage step is accomplished, the final mask and bounding box have been generated.

>>>>

%abstract can be shortened a good bit.
%can offer an alternative manana..
\begin{abstract}
Metadata are key descriptors of research data, particularly for researchers seeking to apply machine learning (ML) to the vast collections of digitized specimens. Unfortunately, the available metadata is often sparse and, at times, erroneous. Additionally, it is prohibitively expensive to address these limitations through traditional, manual means. This paper reports on research that applies machine-driven approaches to analyzing digitized fish images and extracting various important features from them. The digitized fish specimens are being analyzed as part of the Biology Guided Neural Networks (BGNN) initiative, which is developing a novel class of artificial neural networks using phylogenies and anatomy ontologies. Automatically generated metadata is crucial for identifying the high-quality images needed for the neural network's predictive analytics. Methods that combine ML and image informatics techniques allow us to rapidly enrich the existing metadata associated with the 7,244 images from the Illinois Natural History Survey (INHS) used in our study. Results show we can accurately generate many key metadata properties relevant to the BGNN project, as well as general image quality metrics (e.g.\ brightness and contrast). Results also show that we can accurately generate bounding boxes and segmentation masks for fish, which are needed for subsequent machine learning analyses. The automatic process outperforms humans in terms of time and accuracy, and provides a novel solution for leveraging digitized specimens in ML. This research demonstrates the ability of computational methods to enhance the digital library services associated with the tens of thousands of digitized specimens stored in open-access repositories world-wide.
% OLD text - Over the last several decades advances in computing, imaging, and cyberinfrastructure have had a major impact on scientific research and discovery. One area of considerable activity is the digitization of the biological specimens that have been acquired worldwide by museums and other research institutions, undertakings that have produced large image collections.The metadata that is vital for subsequent ML, analysis and scientific discovery based on these specimen image repositories is often unavailable, sparse or incorrect. As a step towards improving metadata in specimen research image collections, our team is developing methods for automatically analyzing fish images to extract a variety of important features. These fish specimens are being studied for a larger project entitled Biology Guided Neural Networks (BGNN), which is developing a novel class of artificial neural networks that can exploit the machine readable and predictive knowledge about biology that is available in specimen images, phylogenies and anatomy ontologies. Using a combination of ML and image informatics tools and techniques, we can accurately determine metadata such as fish quantity and location within images, fish orientation and other quantitative fish features, image scaling based on ruler identification and measurement, and general image quality metrics for a substantial number of the images being used in the BGNN project.Our goal is to develop image metadata generation methods that both support the research underway within the BGNN project, and provide a framework for future technology developments that can be deployed by repository curators to improve and bolster the metadata they provide with their specimen images. A longer term goal is to extend the image analysis methods for computing quantitative features in support of specific biological investigations.
\end{abstract}

@@

\section{Introduction}
% Moving teaser since this template doesn't actually ask for one
Over the last several decades advances in computing, imaging, and cyberinfrastructure have supported the growth of digital natural history collections, many of which contain specimen images~\cite{beaman2012mass}. Additionally, initiatives, such as the National Science Foundation’s Advancing Digitization of Biodiversity Collections (ADBC) program,
% (which ran for nearly a decade),
have supported the digitization and curation of tens of thousands of biological specimens~\cite{page2015digitization}. These digitized specimens are generally accessible through global, open-access repositories that support digital library services, such as browsing, search and retrieval, and preservation. The digitized renderings of these rich collections permit researchers, educators, students, and the general public to examine biological specimens
on a previously unattainable scale. Moreover, the digitized instantiations present a pathway  for making new scientific discoveries via the application of machine learning (ML).

Unfortunately, potential scientific advances are hindered by image quality
problems and the lack of accurate and pertinent metadata
associated with the image collections.
Poor quality images (e.g.\ low contrast, inadequate lighting,
out-of-focus or cluttered visual arrangements) are inadequate
for automated
image analysis by ML algorithms and lead to inferior
computational results.
In order to perform quantitative morphometric analysis of the specimens,
the physical scale of the images (\(\frac{\mathrm{pixels}}{\mathrm{cm}}\)) is needed; thus
requiring the ability to identify and take measurements using rulers in the images.
Many specimen collections do include Darwin Core metadata~\cite{biodiv_info_standards}, detailing
specimen taxon, geographic location, and several other specimen-related aspects.
Additionally, some digitization efforts record technical metadata, detailing imaging specifications. While these types of metadata are helpful for a
human examining several images at a time, they are insufficient for researchers seeking to apply computational methods %ML? or okay here
to examine thousands of images
to determine if, for example, a specific fish grows to different lengths
in different habitats, or to study differences in the size of a particular anatomical feature,
e.g.~the size of a dorsal fin.
\begin{figure}[t]
  \centering
  % \includegraphics[width=.31\linewidth]{images/INHS_FISH_100314}
  % \hspace{1mm}
  \includegraphics[width=.95\linewidth]{images/INHS_FISH_100682}
  % \hspace{1mm}
  % \includegraphics[width=.31\linewidth]{images/INHS_FISH_100020}
  \caption{An image from the Illinois Natural History Survey (INHS) collection.}
  \label{fig:INHS_examples}
\end{figure}

Since digital collections may each contain tens of thousands of images, manually producing image-related metadata for each digitized specimen is prohibitively expensive. Methods for automatically computing metadata are therefore needed to fully exploit biological image repositories for scientific discovery.
%we are both extracting and calculating. Just to double check then, our definition/understanding of computing here includes both of these, or should we focus on extraction, with the idea that calculating is the extra novel thing added, the application of math-the groovy stuff you guys added.  
As a step towards improving metadata in research specimen image collections, members of Drexel University's Metadata Research Center are developing methods to automatically analyze fish images and
extract a set of data features that provide important metadata about the
digitized specimens.
The research is being conducted as part of the Biology Guided Neural Networks (BGNN) project, which is developing a novel class of artificial neural networks that exploit machine readable and predictive knowledge associated with specimen images, phylogenies and anatomy ontologies.
Using a combination of ML and image informatics 
techniques,
%tools and [okay to just say image informatics techniques instead of "image informatics tools and techniques" - thinking techniques implies tools.]
we can accurately determine general image quality and metadata, such as fish quantity, location and orientation, and
image scaling based on ruler identification and measurement. Image scaling
allows us to compute quantitative features about the fish specimens, such
as their length and area.  In order to test and validate our methods, they
have been  applied to a set of \(7,244\)
images drawn from the Illinois Natural History Survey (INHS) Collection of fish specimens~\cite{INHS}.
Figure \ref{fig:INHS_examples} presents a typical image used in our
study.
%Dave/Joel, the section above, from "we can accurately ..." to the figures" to me is more results. I guess it's okay to give this in introduction. Just wanted to raise this point. I sometimes give a paraphrase too, but just good to see if it is a little too much or okay with you both. I think it's okay as I re-read it, but good to have someone check.
The following section of the paper provides contextual background for this work, followed by the research goals and objectives, and a review of our research methods. Next, the results, along with discussion, are presented. The conclusion highlights key findings and identifies next steps.

\section{Related Work}
\subsection{Metadata for Natural History Image Collection}
%question/comment - we need to keep in mind we are deal with digitized specimens, not simply digital, in other words, the artifacts themselves are digital version of physical, not like an x-ray, where the image is digital from the start.  
A number of different metadata standards have been applied to support the description and access of digital images of scientific specimens. The Darwin Core (DwC)~\cite{biodiv_info_standards}, developed specifically to describe biological diversity data, is one of the most popular standards for such efforts. It is an extension of the Dublin Core's DCMI Metadata Terms~\cite{dc_terms}.
The Audubon Core~\cite{audub_core}, which supports the discoverability, dissemination, and use of data related to biological organisms (including 3--D digitized specimens), is a DwC extension that has become the popular metadata standard for biodiversity multimedia resources and collections. All of these descriptive standards and extensions include metadata properties for taxon, geographic location, and other important specimen content, and have been developed primarily from the perspective of a human curator. In other words, their application anticipates that a curator or data entry staff will manually generate metadata, drawn from acquisition logs or original specimen labels. The generated metadata associated with each digital rendering is generally sparse and prone to human error, placing limitations on a researcher seeking to apply ML to the image and the metadata for scientific research.

This limitation is magnified when trying to assess the actual quality of the digitized specimen. Descriptive-oriented standards support search and retrieval, and the biodiversity community has advocated for data fitness standards \cite{chapman2020developing}. This point is also emphasized by
Wieczorek et al.~\cite{wieczorek2012darwin} in their report on the variety of DwC metadata extensions needed to meet growing community concerns and
requirements, including data quality and fitness. Even so, metadata describing image quality is severely limited and generally missing. This point is addressed in detail by Leipzig et al.~\cite{leipzig2021biodiversity} and serves as the rationale for Tulane University's effort to manually capture
content for 22 metadata properties that characterize digitized specimen image quality. Their work is being conducted in connection with the larger BGNN initiative, and the difficulties encountered during the process underscore the need to explore automatic metadata generation methods.
%Fish species dataset in Pakistan Shah 2019 \cite{Shah2019FishPakFS}
\subsection{Automatic Metadata Generation}
Advances in automatic metadata generation of both descriptive and technical metadata are relevant to the research presented in this paper. Automatic metadata generation of descriptive bibliographic data has been a research focus for close to 20 years \cite{liddy2002automatic,greenberg2004metadata,cardinaels2005automating,paynter2005developing}. Researchers have applied support vector machine (SVM) approaches~\cite{han2003automatic}, and associated networks to address sparse and incomplete metadata~\cite{rodriguez2009automatic}, and various successes are integrated into day-to-day workflows. Heidorn, et al.~\cite{heidorn2008automatic} demonstrated the use of optical character recognition (OCR) to extract specimen information from the original typed and often hand-annotated labels that are digitized along with herbarium collection holdings. The extracted information was encoded in the DwC metadata associated with the specimen's digitized rendering. There has also been some success with extracting descriptive cartographic information from maps~\cite{manso2004automatic}. While descriptive metadata covers taxon, geographic location, and other important aspects, and may even record the image format; uses of automatic processes are still limited. More significantly, descriptive metadata does not sufficiently addressed data quality.

@@

application of technology for marine science, in the study of aquatic

@@

combinations of feature extractions, input classifiers and clustering

@@

types of fish with 92\% accuracy.

@@

accuracy when identifying 15 different fish species in challenging underwater

@@

\begin{comment}

@@

\end{comment}

The research reviewed above demonstrates the application of image feature extraction and
machine learning algorithms to fish images; although researchers have not applied these approaches to the numerous collections of digitized specimens accessible in open repositories.  Our research addresses this need by applying ML and informatics techniques to extract key metadata properties from the images.
% further computing higher-level metadata based on these initial results.
The availability of general and powerful
off-the-shelf ML tools make the usage of previous special-purpose techniques unnecessary.
% Our goals and objectives are presented in the following section.

\begin{comment}
The research reviewed above involves image features extraction and
artificial intelligence; although the researchers have not applied these
approaches to the burgeoning collections of digitized specimens
accessible in open repositories. Our research addresses this need by
applying ML and image informatics techniques to extract key
metadata properties from fish specimen images and computing
higher-level metadata based on these initial results.
Our goals and objectives our presented below.

Our work stands apart from previous work in that we are
addressing a different need: lack of metadata is impeding scientific studies.
Our focus and motivation are different.
Effectively doing the computational pre-processing
that will enable further downstream analyses.

@@

Digitized specimens accessible in open-access repositories provide a rich,
extensive data source for ML and scientific discovery.
These resources, however, remain largely untapped due to image quality
issues and metadata limitations.
The overall goal of our work addresses this need by
% combining ML and image informatics techniques to produce
developing a computational
% . The overall goal of our research is to offer a machine-driven [*novel/innovative?? blah...]
alternative to the current manual metadata generation process, which is
prohibitively costly both in terms of labor and time. Additionally, our
methods collectively provide a novel and general approach to computing
higher-level metadata that will support scientific inquiry based
on the analysis of specimen image collections.

@@

\item Investigate image processing at the pixel level.
Pilot testing found that \verb|detectron| undersegmented the detected objects
with tightly enclosing bounding boxes. We will determine if
pixel analysis methods commonly found in image informatics may produce
more accurate bounding boxes and object masks.
% background as part of the fish, or the
% bounding box may clip away part(s) of the fish with
The specific aims of this objective are to:
%not sure we have to list all the details, but something like the below, with the 4 aspects of pixel analysis we tested/investigate/experimented with

@@

\item
Automatically determine when modified methods fail and \verb|detectron| values
should be used as is.
% Developing a fallback approach for when flood fill operations behave unexpectedly the image is too washed out.
\end{enumerate}

@@

%In order to address the need for fish specimen image metadata that can support scientific investigations we have begun the deployment of both off-the-shelf and custom-written software that automatically generates a variety of metadata from a publicly-available biological image repository.  The types of metadata being produced are related to image quality, content and scale, and should provide the information necessary for advanced quantitative studies of the digitized specimens.
\begin{figure}[t]
  \centering
 % \includegraphics[width=.45\linewidth]{images/teaser1_crop}
  % \hspace{5mm}
  \includegraphics[width=.95\linewidth]{images/teaser2_crop}
  \caption{Initial object detection on a specimen image using Detectron2~\cite{wu2019detectron2}.}
  \label{fig:teaser}
\end{figure}

The automated metadata generation methods for our project were developed to work on a specific set of images from the INHS\ Fish Collection~\cite{INHS}.  Most of these images have been configured, produced and acquired with a standard procedure.  The images used for our study contain one fish placed on a bright, white background and contain an information tag and the same ruler.  See Figure \ref{fig:INHS_examples} for an example image from the collection. While training and focusing our system on images with very similar compositions and visual properties may limit its immediate applicability, our efforts demonstrate the potential that ML and image informatics techniques have for automatically generating metadata for biological specimen image collections in general.

@@

\subsection{Detectron}
A prerequisite task to performing any advanced metadata property generation
is finding the specimens (and other relevant objects) within the collection
images. Object detection has been a broadly active field of study in recent
years \cite{zou2019object}, and has resulted in a number of well-tested, purpose-built architectures. We elected to use Facebook AI Research's (FAIR)
\verb|detectron| tool \cite{wu2019detectron2}, and specifically its implementation of the Mask R-CNN architecture \cite{he2018mask}, for object detection in our project, given its many flexible and robust capabilities. Most importantly, following a review of the literature and available tools, we determined that there were no other machine learning packages that returned pixel by pixel masks over detected objects in a comparable fashion.

\verb|detectron| is built on \verb|pytorch|~\cite{NEURIPS2019_9015} and provides a relatively straightforward method for training on COCO~\cite{DBLP:journals/corr/LinMBHPRDZ14} format datasets. It is able to handle any number of object classes, and can classify an arbitrary number of objects within a given image. We chose \verb|detectron| for its relative ease of use compared to lower level libraries, and its implementation of powerful architectures developed by FAIR.
For our project, we use it to identify five object classes: fish, fish eyes, rulers, and the numbers 2 and 3 on rulers,
as shown in Figure \ref{fig:teaser}. Objects with a 30\% confidence score or higher are maintained for analysis.

@@

\begin{table*}[t]
    \centering
    \caption{Metadata properties (* indicates higher order derived properties)}
    \label{tab:properties}
    \begin{tabular}{cccp{0.5\linewidth}}
        \toprule
        \textbf{Property} & \textbf{Association} & \textbf{Type} & \textbf{Explanation}\\
        \midrule
        \verb|has_fish| & Overall Image & Boolean & Whether a fish was found in the image.\\
        \verb|fish_count| & Overall Image & Integer & The quantity of fish present.\\
        \verb|has_ruler| & Overall Image & Boolean & Whether a ruler was found in the image.\\
        \verb|ruler_bbox| & Overall Image & 4 Tuple & The bounding box of the ruler (if found).\\
        \verb|scale|* & Overall Image & Float & The scale of the image in \(\frac{\mathrm{pixels}}{\mathrm{cm}}\).\\
        \verb|bbox| & Per Fish & 4 Tuple & The top left and bottom right coordinates of the bounding box for a fish.\\
        \verb|background.mean| & Per Fish & Float & The mean intensity of the background within a given fish's bounding box.\\
        \verb|background.std| & Per Fish & Float & The standard deviation of the background within a given fish's bounding box.\\
        \verb|foreground.mean| & Per Fish & Float & The mean intensity of the foreground within a given fish's bounding box.\\
        \verb|foreground.std| & Per Fish & Float & The standard deviation of the foreground within a given fish's bounding box.\\
        \verb|contrast|* & Per Fish & Float & The contrast between foreground and background intensities within a given fish's bounding box.\\
        \verb|centroid| & Per Fish & 4 Tuple & The centroid of a given fish's bitmask.\\
        \verb|primary_axis|* & Per Fish & 2D Vector & The unit length primary axis (eigenvector) for the bitmask of a given fish.\\
        \verb|clock_value|* & Per Fish & Integer & Fish's primary axis converted into an integer ``clock value'' between 1 and 12.\\
        \verb|length|* & Per Fish & Float & The length of a fish in centimeters.\\
        \verb|mask| & Per Fish & 2D Matrix & The bitmask of a fish in 0's and 1's.\\
        \verb|pixel_analysis_failed| & Per Fish & Boolean & Whether the pixel analysis process failed for a given fish. If \verb|true|, \verb|detectron|'s mask and bounding box were used for metadata generation.\\
        \verb|score| & Per Fish & Float & The percent confidence score output by \verb|detectron| for a given fish.\\
        \verb|has_eye| & Per Fish & Boolean & Whether an eye was found for a given fish.\\
        \verb|eye_center| & Per Fish & 2 Tuple & The centroid of a fish's eye.\\
        \verb|side|* & Per Fish & String & The side (i.e.\ \verb|'left'| or \verb|'right'|) of the fish that is facing the camera (dependent on finding its eye).\\
      \bottomrule
\end{tabular}
\end{table*}

@@

\subsubsection{Adjusting the Bounding Box}
With an accurate mask generated, it is then necessary to check whether the bounding box needs to be expanded or shrunk along any of its edges.
Expansion is done first, by checking whether any edge intersects with any of the foreground mask pixels. If one does, it is expanded out by 1 pixel. If any edges are expanded, the whole process of masking and expansion is repeated to account for any changes in average intensities. Once no edges contain foreground pixels, the bounding box is then shrunk.
% This process is more efficient as all that is required is to shrink
Each edge is contacted by one pixel until it contains one or more foreground pixels. Once the shrinkage step is accomplished, the final mask and bounding box have been generated.
